Writing Trash Bin

### 2024-08-19 writingdumpster.qmd
added gt table to writing dumpster

>>>>

# GT table code
```{r}
#| echo: false
#| message: false
#| warning: false
# Make nice table
example_table <- my_map_data |>
  mutate(variance = sqrt(variance)) |>
  select(c(count_id, county_name, temp, variance_class, variance)) |>
  as_tibble()|>
  pivot_wider(id_cols=c(count_id, county_name, temp,), 
              names_from = variance_class, 
              values_from = variance) |>
  head()|>
  gt() |>
   tab_header(
    title = "Average Daily High Temperatures of Iowa Counties",
    subtitle = "Psudo-data with high standard error and low standard error cases") |>
  tab_spanner(
    label = "Standard Error",
    columns = c(highvar, lowvar)
  ) |>
  cols_label( 
    count_id = "ID", 
    county_name  = "County",
    temp = "Temperature (°C)",
    highvar = "High",
    lowvar = "Low"
    ) |>
  fmt_number(columns = c(temp, highvar, lowvar)) |>
  data_color(
    columns = temp,
    method = "numeric",
    palette = "Oranges",
    domain = c(21, 29)
  ) |>
  data_color(
    columns = c(highvar, lowvar),
    method = "numeric",
    palette = "Greens",
    domain = c(0, 3)
  ) |>
  as_latex()
```
